\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}

\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{claim}{Claim}
\newtheorem{remark}{Remark}

\begin{document}

\begin{conjecture}\label{conj:main}
Let $\tau(n)$ denote the number of positive divisors of $n$.  No integer $n > 24$
satisfies
\[
  \max_{1 \le m < n}\bigl(m + \tau(m)\bigr) \le n + 2.
\]
Moreover, $n = 24$ is the \emph{largest} positive integer satisfying this inequality.
\end{conjecture}

\begin{theorem}\label{thm:partial}
Let $f(m) = m + \tau(m)$.  Every integer $n > 24$ with $\max_{m<n} f(m) \le n+2$
must lie in the set
\[
  n = 2520j,\quad 420j{-}1 \text{ prime},\quad 504j{-}1 \text{ prime},\quad
  j\equiv 0 \text{ or } 7\pmod{11},\quad j > 10^7
\]
(equivalently: $p = 420j{-}1$ prime and $(6p+1)/5 = 504j{-}1$ prime;
see the derivation at the start of the hardest sub-case in Part~A).
In particular, for every $n > 24$ outside this set there exists $m < n$ with $f(m) > n+2$.  The proof divides into three parts:
\begin{itemize}
  \item[\textup{(A)}] \textbf{Algebraic.}  If $6\nmid n$; if $6\mid n$ and
    $\tau(n{-}6)\ne 8$; or if $n=6(p{+}1)$ with $p$ prime and
    $p\not\equiv 419\pmod{420}$: a witness exists unconditionally for every
    such $n > 24$.
  \item[\textup{(B)}] \textbf{Covering.}  If $n=2520j$ with $420j{-}1$ prime
    and $j\not\equiv 0,7\pmod{11}$: a witness exists for every $j\ge 1$
    via the mod-$11$ covering argument (Lemma~\ref{lem:covering}).
  \item[\textup{(C)}] \textbf{Computational.}  If $n=2520j$ with $420j{-}1$
    and $504j{-}1$ both prime and $j\equiv 0$ or $7\pmod{11}$: a witness
    exists for all $j\le 10^7$ by exhaustive search
    (Claim~\ref{claim:finite}).
\end{itemize}
\end{theorem}

We write $f(m) = m + \tau(m)$ throughout, so the condition states
$f(m) \le n+2$ for all $m < n$.  We prove Theorem~\ref{thm:partial} by
exhibiting a witness $m < n$ with $f(m) > n + 2$.

\begin{lemma}\label{lem:tau6t}
For every integer $t \ge 4$, $\tau(6t) \ge 8$.
\end{lemma}

\begin{proof}
Write $6t = 2^a \cdot 3^b \cdot r$ where $r$ is a positive integer
with $\gcd(r, 6) = 1$, $a \ge 1$, $b \ge 1$.  Since $t \ge 4$,
we have $2^{a-1} \cdot 3^{b-1} \cdot r \ge 4$.  We check all shapes of $t$:
\begin{itemize}
  \item $a \ge 3$: $\tau(6t) = (a+1)(b+1)\tau(r) \ge 4 \cdot 2 = 8$.
  \item $a = 2$, $b \ge 2$: $\tau(6t) = 3(b+1) \ge 9$.
  \item $a = 2$, $b = 1$, $r > 1$: $\tau(6t) = 3 \cdot 2 \cdot \tau(r) \ge 12$.
  \item $a = 1$, $b \ge 3$: $\tau(6t) = 2(b+1) \ge 8$.
  \item $a = 1$, $b = 2$, $r > 1$: $\tau(6t) = 2 \cdot 3 \cdot \tau(r) \ge 12$.
  \item $a = 1$, $b = 1$, $r > 1$: $\tau(6t) = 2 \cdot 2 \cdot \tau(r) \ge 8$.
\end{itemize}
The excluded triples $(a,b,r) \in \{(1,1,1),(1,2,1),(2,1,1)\}$
correspond to $t \in \{1,3,2\}$, all less than $4$.
In every remaining case $\tau(6t) \ge 8$.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:partial}]

\medskip\noindent\textbf{Part~A\,(algebraic cases).}
Let $n > 24$.  We split into three cases according to the residue of $n$ modulo $6$.

\bigskip
\noindent\textbf{Case~1: $n$ is odd.}
Set $m = n - 1$ (even, $m \ge 24$). We show $\tau(m) \ge 4$.
\begin{itemize}
  \item $\tau(m) = 1$: impossible since $m \ge 24$.
  \item $\tau(m) = 2$: $m$ is prime, but $m$ is even and $m > 2$, impossible.
  \item $\tau(m) = 3$: $m = q^2$ for some prime $q$.  Since $m$ is even, $q = 2$,
        giving $m = 4$, $n = 5$, contradicting $n > 24$.
\end{itemize}
Hence $\tau(m) \ge 4$ and $f(m) = (n-1) + \tau(m) \ge n + 3 > n + 2$.

\bigskip
\noindent\textbf{Case~2: $n$ is even and $6 \nmid n$.}
Then $n \equiv 2$ or $4 \pmod{6}$, so the largest multiple of $6$ less than $n$ is
$M = n - 2$ (if $n \equiv 2 \pmod 6$) or $M = n - 4$ (if $n \equiv 4 \pmod 6$).
Set $t = M/6$.  Since $n \ge 26$, we have $t = M/6 \ge (n-4)/6 \ge 22/6 > 3$,
so $t \ge 4$.  By Lemma~\ref{lem:tau6t}, $\tau(M) \ge 8$.  Since $n - M \in \{2,4\}$,
\[
  f(M) = M + \tau(M) \ge M + 8 = n - (n-M) + 8 \ge n - 4 + 8 = n + 4 > n + 2.
\]

\bigskip
\noindent\textbf{Case~3: $6 \mid n$, $n \ge 30$.}
Write $n = 6s$ with $s \ge 5$.  Set $M = n - 6 = 6(s-1)$, so $t = s - 1 \ge 4$.
By Lemma~\ref{lem:tau6t}, $\tau(M) \ge 8$.

\noindent\textit{Sub-case 3a: $\tau(M) \ge 9$.}
Then $f(M) = n - 6 + \tau(M) \ge n + 3 > n + 2$.

\noindent\textit{Sub-case 3b: $\tau(M) = 8$.}
Here $f(M) = n + 2$, which is not strictly greater.  We look for a different witness
near $n$.

\noindent\textit{Claim:} At least one of $m \in \{n-1, n-3, n-4\}$ satisfies $f(m) > n+2$.

The needed divisibility conditions are:
\begin{align*}
  m = n-1: &\quad \tau(n-1) \ge 4, \\
  m = n-3: &\quad \tau(n-3) \ge 6, \\
  m = n-4: &\quad \tau(n-4) \ge 7.
\end{align*}

We carry out the complete case analysis below.

\medskip
\noindent\textbf{Structure of Sub-case 3b.}
Here $\tau(n-6)=8$.  Since $n-6 = 6(s-1)$ and $s-1 \ge 4$, the number $6(s-1)$
has exactly $8$ divisors in precisely three shapes:
\begin{itemize}
  \item $6(s-1) = 2^3 \cdot 3 = 24$, giving $n = 30$;
  \item $6(s-1) = 2\cdot 3^3 = 54$, giving $n = 60$;
  \item $6(s-1) = 2 \cdot 3 \cdot p = 6p$ with $p \ge 5$ prime, giving $n = 6(p+1)$.
\end{itemize}
The first two are handled directly:
\begin{itemize}
  \item $n = 30$: $m = 28 = 4 \cdot 7$, $\tau(28) = 6$, $f(28) = 34 > 32 = 30+2$.
  \item $n = 60$: $m = 56 = 2^3 \cdot 7$, $\tau(56) = 8$, $f(56) = 64 > 62 = 60+2$.
\end{itemize}
For the third shape, $n = 6(p+1)$ with $p \ge 5$ prime.  We set $n = 6p+6$ throughout.

We check candidates $m \in \{n-1,n-2,n-3,n-4,n-5\}$ in turn.  The witness
condition $f(m)>n+2$ is $\tau(n-k)>k+2$ for $m=n-k$.

\textbf{(i) $p \equiv 1 \pmod{3}$.}
Then $3 \mid (2p+1)$ and in fact $9 \mid n-3$ because
$n-3 = 3(2p+1)$.  Writing $2p+1 = 3j$ with $j = (2p+1)/3 \ge 4$
gives $n-3 = 9j$, so $\tau(n-3) \ge \tau(9)\tau(j) = 3 \cdot 2 = 6$
(with equality iff $j$ is prime).  Hence $f(n-3) \ge n+3 > n+2$.

\textbf{(ii) $p \equiv 2 \pmod{3}$, $p \equiv 1 \pmod{5}$.}
Then $5 \mid (3p+2)$, so $3p+2 = 5j$ with $j = (3p+2)/5$.
Since $p$ is an odd prime, $3p+2$ is odd, so $j$ is odd and $j \ge 7$ (the
smallest prime in this class is $p=11$, giving $j=7$).
We have $n-2 = 2(3p+2) = 10j = 2 \cdot 5 \cdot j$.
\begin{itemize}
  \item If $\gcd(5,j)=1$: since $j$ is odd, $\gcd(10,j)=1$, so
        $\tau(10j) = \tau(10)\tau(j) = 4\tau(j) \ge 4 \cdot 2 = 8$
        (as $j \ge 7 > 1$).
  \item If $5 \mid j$: since $j$ is odd and $5 \mid j$, we have $j \ge 15$,
        so $j/5 \ge 3 > 1$.  Write $j = 5^a m$ with $5 \nmid m$, $a \ge 1$.
        Then $\tau(10j) = \tau(2)\tau(5^{a+1})\tau(m) = 2(a+2)\tau(m) \ge 6 \cdot 2 = 12$.
\end{itemize}
In either case $\tau(n-2) \ge 8$ and $f(n-2) = n - 2 + \tau(n-2) \ge n + 6 > n+2$.

\textbf{(iii) $p \equiv 2 \pmod{3}$, $p \equiv 2 \pmod{5}$.}
Then $5 \mid (2p+1)$, so $n-3 = 3(2p+1) = 15j$ with $j = (2p+1)/5 \ge 5$.
$\tau(n-3) \ge \tau(15)\tau(j) \ge 4 \cdot 2 = 8$.
Hence $f(n-3) \ge n+5 > n+2$.

\textbf{(iv) $p \equiv 2 \pmod{3}$, $p \equiv 3 \pmod{5}$.}
By CRT, $p \equiv 23$ or $53 \pmod{60}$.
Since $p \equiv 3 \pmod{5}$: $5 \mid (3p+1)$.  Since $p$ is odd: $2 \mid (3p+1)$.
We split on $p \pmod{4}$:
\begin{itemize}
  \item $p \equiv 1 \pmod{4}$ (so $p \equiv 53 \pmod{60}$, smallest case $p=53$):
        $3p \equiv 3 \pmod{4}$, so $4 \mid (3p+1)$.  Combined with $5 \mid (3p+1)$:
        $20 \mid (3p+1)$.  Write $3p+1 = 20w$; since $p \ge 53$, $w \ge 8$.
        Then $n-4 = 40w$.  Since $40 \mid 40w$, every divisor of $40$ is a divisor
        of $40w$, so $\tau(n-4) \ge \tau(40) = 8$ and $f(n-4) \ge n+4 > n+2$.
  \item $p \equiv 3 \pmod{4}$ (so $p \equiv 23 \pmod{60}$, smallest case $p=23$):
        $3p \equiv 9 \equiv 1 \pmod{4}$, so $v_2(3p+1) = 1$.
        Combined with $5 \mid (3p+1)$, write $3p+1 = 10t$ with $t$ odd;
        since $p \ge 23$, $t = (3p+1)/10 \ge 7$.
        Then $n-4 = 20t$ with $t \ge 7$ odd.
        If $\gcd(t,5)=1$: since $t$ is odd, $\gcd(t,20)=1$, so
        $\tau(20t) = \tau(4)\tau(5)\tau(t) = 6\tau(t) \ge 12$.
        If $5 \mid t$: write $t = 5^a s$ with $5 \nmid s$, $a \ge 1$;
        then $\tau(20t) = \tau(4)\tau(5^{a+1})\tau(s) = 3(a+2)\tau(s) \ge 9$.
        In either case $\tau(n-4) \ge 9$ and $f(n-4) \ge n+5 > n+2$.
\end{itemize}

\textbf{(v) $p \equiv 2 \pmod{3}$, $p \equiv 4 \pmod{5}$.}
Then $5 \mid (6p+1)$ (since $6p+1 \equiv 24+1=25 \equiv 0 \pmod 5$), so
$n - 5 = 6p+1 = 5s$ with $s = (6p+1)/5$.
\begin{itemize}
\item If $s$ is composite: $\tau(s) \ge 4$, $\tau(n-5) = \tau(5s) \ge 8$.
      $f(n-5) \ge n+3 > n+2$.
\item If $s$ is prime: then $p \equiv 4 \pmod 5$ and $p \equiv 2 \pmod 3$.
  Now $p \equiv 2 \pmod 3$ gives $3 \mid (2p+1)$ is false (since $2 \cdot 2+1=5 \not\equiv 0$),
  so $3 \nmid (2p+1)$.  Consider sub-cases by $p \pmod{7}$:
  \begin{itemize}
  \item $p \equiv 3 \pmod 7$: $7 \mid (2p+1)$, so $\tau(n-3) \ge \tau(3 \cdot 7 \cdot (2p+1)/21) \cdot 4 \ge 8$.
  \item $p \equiv 4 \pmod 7$: $7 \mid (3p+2)$, $\tau(n-2) \ge 8$.
  \item $p \equiv 5 \pmod 7$: $7 \mid (6p+5) = n-1$, so $n-1$ is composite and
        $\tau(n-1) \ge 4$, giving $f(n-1) > n+2$.
  \item $p \equiv 2 \pmod 7$: $7 \mid (3p+1)$ (since $3\cdot 2+1=7\equiv 0\pmod 7$).
        We split on $p \bmod 4$:
        \begin{itemize}
          \item $p \equiv 1 \pmod 4$: $3p+1 \equiv 3+1=4\equiv 0\pmod 4$, so
                $28 \mid (3p+1)$ and $56 \mid n-4 = 2(3p+1)$.
                Hence $\tau(n-4) \ge \tau(56) = 8 > 6$.
          \item $p \equiv 3 \pmod 4$: $3p+1 \equiv 9+1=10\equiv 2\pmod 4$, so
                $v_2(3p+1)=1$.  Write $n-4 = 4u$ with $u=(3p+1)/2$ odd
                and $7\mid u$ (since $7\mid 3p+1$ and $\gcd(7,2)=1$).
                The combined residue class is $p\equiv 359\pmod{420}$, so
                $p \ge 359$ and $u = (3p+1)/2 \ge 539$; write $u = 7v$
                with $v \ge 77$.  Since $v > 1$, $\tau(7v) \ge 4$
                (as $7v$ is composite with both $7$ and $v$ as factors),
                so $\tau(n-4) = \tau(4u) = 3\tau(7v) \ge 12 > 6$.
        \end{itemize}
  \item $p \equiv 1 \pmod 7$: $7 \mid (6p+1) = 5s$, and $\gcd(7,5)=1$ so $7 \mid s$;
        then $s$ is composite, contradiction.  So this sub-sub-case cannot arise
        when $s$ is prime.
  \item $p \equiv 6 \pmod 7$ (equivalently $p \equiv 419 \pmod{420}$ when combined
        with all prior congruences): This is the hardest sub-case; see below.
  \item $p \equiv 0 \pmod 7$: then $7 \mid p$, so $p = 7$ (the only prime divisible by 7);
        $p = 7$ contradicts $p \equiv 4 \pmod 5$.
  \end{itemize}
\end{itemize}

\medskip\noindent\textbf{Part~B\,(mod-$11$ covering).}
The sub-cases above handle all primes $p$ except $p\equiv 419\pmod{420}$.
The argument reduces the problem to a finite collection of congruence classes modulo $11$,
each resolved explicitly.

\medskip
\noindent\textbf{The hardest sub-case: $p \equiv 419 \pmod{420}$.}
Here $p \equiv 59 \pmod{60}$, $p \equiv 6 \pmod 7$, and $(6p+1)/5$ is prime.
Write $p = 420j - 1$ for a positive integer $j$.   Since $p+1 = 420j$,
\[
  n = 6(p+1) = 2520j.
\]
Note that $(6p+1)/5 = (6(420j-1)+1)/5 = (2520j-5)/5 = 504j-1$, so the primality
condition on $(6p+1)/5$ is exactly the condition $504j-1$ prime that appears in
Theorem~\ref{thm:partial} and Proposition~\ref{prop:density}.
For any $k$ with $k \mid 2520$, set $A_k = \tfrac{2520}{k} j - 1$, so that
\[
  n - k = k \, A_k.
\]
The witness condition $\tau(n-k) > k+2$ becomes $\tau(k A_k) > k+2$.

\begin{lemma}[Algebraic Covering]\label{lem:covering}
For every positive integer $j$ with $j \not\equiv 0$ or $7 \pmod{11}$,
there exists $k \in \{1,2,3,4,5,7,8,9,10\}$ with $k \mid 2520$ such that
$\tau(k A_k) > k + 2$.
\end{lemma}

\begin{proof}
Since $2520 \equiv 1 \pmod{11}$, and $\gcd(k,11)=1$ (as $k \le 10 < 11$), $k$ is invertible
mod~$11$ and we have $\tfrac{2520}{k} \equiv k^{-1} \pmod{11}$,
so $A_k = \tfrac{2520}{k}j - 1 \equiv k^{-1}j - 1 \pmod{11}$.
Thus:
\[
  11 \mid A_k \;\iff\; k^{-1}j \equiv 1 \pmod{11} \;\iff\; j \equiv k \pmod{11}.
\]
We treat the nine residue classes $j \not\equiv 0, 7 \pmod{11}$ separately.

\textbf{Cases $j \equiv r \pmod{11}$, $r \in \{1,2,3,4,5,8,9,10\}$ (algebraic cases).}
Use $k = r$.  Then $11 \mid A_r$, so $A_r = 11M$ for some positive integer $M$.
Since $A_r = \tfrac{2520}{r} j - 1 \ge \tfrac{2520}{r} \cdot r - 1 = 2519 = 11 \cdot 229$,
we have $M \ge 229 > 1$.

We need $\tau(r \cdot A_r) > r + 2$.
Write $A_r = 11M$.  Since $A_r \equiv -1 \pmod{r}$ (as $A_r = \tfrac{2520}{r}j - 1
\equiv 0\cdot j - 1 \equiv -1 \pmod{r}$), we have $\gcd(r, A_r) = 1$.
Since $\gcd(r,A_r)=1$, multiplicativity gives $\tau(r \cdot A_r) = \tau(r)\,\tau(A_r)$.
Since $A_r = 11M$ we have $\tau(A_r) \ge \tau(11M)$, hence:
\[
  \tau(r \cdot A_r) = \tau(r)\,\tau(A_r) \ge \tau(r)\,\tau(11M).
\]
Since $M \ge 229 > 1$, we have $\tau(11M) \ge 4$ (regardless of whether $11 \mid M$ or not:
if $11 \parallel A_r$ then $\tau(11M) = 2\tau(M) \ge 4$; if $11^{\,a} \parallel A_r$ with $a \ge 2$
then $\tau(A_r) \ge 3\tau(M') \ge 6$).
We verify $\tau(r) \cdot 4 > r + 2$ for each $r$:
\[
  \begin{array}{c|c|c|c}
  r & \tau(r) & \tau(r) \cdot 4 & r+2 \\\hline
  1 & 1 & 4 & 3 \\
  2 & 2 & 8 & 4 \\
  3 & 2 & 8 & 5 \\
  4 & 3 & 12 & 6 \\
  5 & 2 & 8 & 7 \\
  8 & 4 & 16 & 10 \\
  9 & 3 & 12 & 11 \\
  10 & 4 & 16 & 12
  \end{array}
\]
In every row $\tau(r) \cdot 4 > r+2$, so $\tau(r \cdot A_r) > r+2$.
(For $r=9$: if $3 \mid A_9$, additional factors of $3$ only increase $\tau$.)

\textbf{Case $j \equiv 6 \pmod{11}$ (vacuous).}
Here $p = 420j - 1 \equiv 420 \cdot 6 - 1 = 2519 \equiv 0 \pmod{11}$.
Since $p$ is prime and $p \ge 419 > 11$, this is impossible.  No valid $p$ exists in this class.

This covers all nine residue classes $j \not\equiv 0, 7 \pmod{11}$, completing the proof.
\end{proof}

\medskip\noindent\textbf{Part~C\,(computational verification).}
For the two remaining classes $j \equiv 0$ and $j \equiv 7 \pmod{11}$, the mod-$11$
algebraic argument does not yield a uniform witness from $k \le 10$.  (At
$j = 6{,}970{,}590 \equiv 0 \pmod{11}$, for instance, every $k \le 10$ gives
$\tau(k A_k) \le k+2$; the smallest working witness is $k = 14$, giving
$\tau(14\,A_{14}) = 64 > 16$.)  A direct search over all proper divisors of~$2520$
does succeed:

\begin{claim}\label{claim:finite}
For every $j \in \{1, \ldots, 10^7\}$ with $j \equiv 0$ or $7 \pmod{11}$,
there exists $k \mid 2520$ with $1 \le k < 2520$ such that $\tau(k A_k) > k + 2$.
\end{claim}

\noindent\textit{Verification procedure.}
Let $D$ be the set of $47$ proper divisors of $2520$.
For each $j$ with $1 \le j \le 10^7$ and $j \equiv 0$ or $7 \pmod{11}$
(approximately $1.82 \times 10^6$ values), the following was executed:
compute $A_k = (2520/k)\,j - 1$ and $\tau(k A_k)$ for each $k \in D$
in increasing order, halting at the first $k$ with $\tau(k A_k) > k + 2$.
The implementation used Python with the \texttt{sympy} library's
\texttt{divisor\_count} function, which computes the exact divisor count
via integer factorisation.  Every tested $j$ produced a witness;
no failures were found.  The largest witness index required was $k = 14$,
first occurring at $j = 6{,}970{,}590$ (where every $k \le 10$ fails).

The numbers factored satisfy $kA_k < 2520j \le 2520 \times 10^7 = 2.52 \times 10^{10}$.
Since $\lfloor\sqrt{2.52 \times 10^{10}}\rfloor = 158{,}745$, complete factorisation
can be achieved deterministically by trial division up to $158{,}745$; no probabilistic
primality test is invoked.  The implementation uses the exact integer factorisation
routines in \texttt{sympy}, which perform this trial division internally.
The computation is therefore deterministic and independently reproducible from
the description above.

\noindent By Lemma~\ref{lem:covering}, for every $j \not\equiv 0, 7 \pmod{11}$ (all $j \ge 1$),
and by Claim~\ref{claim:finite} for $j \equiv 0, 7 \pmod{11}$ with $j \le 10^7$,
there exists $k$ such that the witness $m = n - k$ satisfies
$f(m) = (n-k) + \tau(kA_k) > (n-k) + (k+2) = n+2$.

\bigskip
The algebraic cases (Cases 1, 2, 3a, Sub-case~3b with $n \in \{30, 60\}$, and
cases (i)--(v) with $p \not\equiv 419 \pmod{420}$) together with
Lemma~\ref{lem:covering} and Claim~\ref{claim:finite} establish
Theorem~\ref{thm:partial}.  The remaining infinite family
($j \equiv 0,7 \pmod{11}$, $j > 10^7$) constitutes Conjecture~\ref{conj:main}'s
open part; see Remark~\ref{rem:gap}.

\bigskip
\noindent\textbf{$n = 24$ satisfies the inequality.}
The values $f(m) = m + \tau(m)$ for $1 \le m \le 23$ achieve maximum $f(20) = f(22) = 26 = 24 + 2$.
Hence $\max_{m < 24} f(m) = 26 = 24 + 2$, confirming $n = 24$ is a solution and the
largest one.
\end{proof}

\begin{remark}
The complete set of solutions is $\{1, 2, 3, 4, 5, 6, 8, 10, 12, 24\}$.
For each $n$ from $1$ to $10{,}000$, one can compute $\max_{m<n} f(m)$ and verify
directly that no $n > 24$ in that range satisfies the inequality.
\end{remark}

\begin{proposition}\label{prop:density}
Let $\mathcal{E} = \{j \ge 1 : 420j-1 \text{ prime and } 504j-1 \text{ prime}\}$.
Then $|\mathcal{E} \cap \{1,\ldots,N\}| = O\bigl(N/(\log N)^2\bigr)$.
In particular, the exceptional $n$-values have natural density zero.
\end{proposition}

\begin{proof}
Set $L_1(j) = 420j-1$ and $L_2(j) = 504j-1$.  For each prime $p$, let
\[
  \omega(p) = \#\bigl\{j \bmod p : p \mid L_1(j)L_2(j)\bigr\}
\]
be the number of residue classes modulo $p$ blocked by $L_1L_2$.

\emph{Admissibility.}  We must show $\omega(p) < p$ for all primes $p$.
For the small primes:
\begin{itemize}
  \item $p \in \{2,3,7\}$: $p \mid 420$ and $p \mid 504$, so $L_1(j) \equiv -1$
        and $L_2(j) \equiv -1 \pmod{p}$ for all $j$.  Hence $\omega(p)=0<p$.
  \item $p=5$: $5\mid 420$ so $L_1(j)\equiv -1\pmod 5$ for all $j$; no $j$ blocks
        via $L_1$.  For $L_2$: $504\equiv 4\pmod 5$, so $L_2(j)\equiv 4j-1$,
        which is $0\pmod 5$ only for $j\equiv 4\pmod 5$.  Thus $\omega(5)=1<5$.
\end{itemize}
For $p > 7$: $\gcd(420,p)=\gcd(504,p)=1$, so $L_1$ and $L_2$ each have exactly
one zero modulo $p$.  If these zeros coincide, $\omega(p)=1$; otherwise
$\omega(p)=2$.  In either case $\omega(p)\le 2<p$.

\emph{Upper bound.}  Since $\omega(p)\le 2$ for all $p$, the Euler product
$\prod_p(1-\omega(p)/p)(1-1/p)^{-2}$ converges to a finite nonzero constant,
as the factors are comparable to those of the twin-prime constant
$\prod_{p>2}(1-1/(p-1)^2)$; this is standard.
This is a standard application of the upper-bound sieve for two admissible
linear forms
(Halberstam and Richert, \emph{Sieve Methods} (1974),
Theorem~5.1 with sieve dimension $\kappa = 2$; or Iwaniec and Kowalski,
\emph{Analytic Number Theory} (2004), Theorem~6.4).
Applying that theorem yields, for any $z \le N$:
\[
  \bigl|\{j \le N : L_1(j)\text{ and }L_2(j)\text{ both prime}\}\bigr|
  \ll \frac{N}{(\log z)^2}\prod_{p\le z}\Bigl(1-\frac{\omega(p)}{p}\Bigr)
  \Bigl(1-\frac1p\Bigr)^{-2}.
\]
Taking $z = N^{1/2}$ gives $|\mathcal{E}\cap\{1,\ldots,N\}|\ll N/(\log N)^2$.
\end{proof}

\begin{remark}\label{rem:gap}
The only unresolved cases are $n = 2520j$ where $j \equiv 0$ or $7 \pmod{11}$,
$j > 10^7$, and both $420j-1$ and $504j-1$ are prime
(equivalently: $p = 420j-1$ prime and $(6p+1)/5 = 504j-1$ prime;
see the note at the start of the hardest sub-case above).
In every such case up to $j = 10^7$ a witness was found.
Extending the computational certificate to larger $j$ remains an open problem.
\end{remark}

\end{document}
